
\documentclass[12pt]{article}


\usepackage{amsmath,amssymb,amsthm}
\usepackage[usenames]{color}
\usepackage{hyperref}
\usepackage{a4wide}

\newcommand{\ici}{National Institute for Research and Development in
  Informatics (ICI), Bucharest}
\newcommand{\imar}{Institute of Mathematics "Simion Stoilow" of the Romanian Academy}

\title{PUBLICATIONS}
\author{Lauren\c tiu Leu\c stean}

\begin{document}
\date{}

\maketitle
\tableofcontents

\section{Books}

\begin{enumerate}
\item {\em Representations of many-valued algebras}, Editura Universitar\u a, Bucharest, 2010, 130pp.
\end{enumerate}


\section{Book Chapters}

\begin{enumerate}
\item {\em An application of proof mining to the proximal point algorithm in CAT(0) spaces} (with  A. Sipo\c s)\\ 
in: A. Bellow, C. Calude, T. Zamfirescu (Editors), Mathematics Almost Everywhere. In Memory of Solomon Marcus, World Scientific, 2018, 153-168.
\item\label{paper-Reich} {\em Nonexpansive iterations in uniformly convex $W$-hyperbolic spaces}, \\
in: A. Leizarowitz, B. S. Mordukhovich, I. Shafrir, A. Zaslavski (Editors),  Nonlinear Analysis and Optimization I: Nonlinear Analysis, Contemporary Mathematics, Vol. 513 (2010), AMS, 193-209.
\end{enumerate}


\section{Journal Papers} \label{journal}


\begin{enumerate}

\item {\em Rates of ($T$-)asymptotic regularity of the generalized Krasnoselskii-Mann-type iteration} (with P. Firmino), \\
Portugaliae Mathematica DOI: https://doi.org/10.4171/PM/2148 (2025)


\item {\em Linear rates of asymptotic regularity for Halpern-type iterations}
(with H. Cheval), \\
Mathematics of Computation, Vol.  94 (2025),  1323-1333.

\item {\em Quantitative asymptotic regularity of the VAM iteration with error terms for $m$-accretive operators in Banach spaces}
(with P. Firmino), \\
Zeitschrift für Analysis und ihre Anwendungen, Vol. 44 (2025), No. 3/4, 501–519.

\item {\em Rates of asymptotic regularity for the alternating Halpern-Mann iteration}
(with P. Pinto), \\
Optimization Letters, Vol. 18  (2024), 529–543.

\item {\em On modified Halpern and Tikhonov-Mann iterations}
(with H. Cheval and U. Kohlenbach), \\
Journal of Optimization Theory and Applications, Vol. 197 (2023), 233--251.

\item {\em Quadratic rates of asymptotic regularity for the Tikhonov-Mann iteration}
(with H. Cheval), \\
Optimization Methods and Software, Vol. 37 (2022), No. 6, 2225--2240.

\item {\em Quantitative results on a Halpern-type proximal point algorithm} (with P. Pinto), \\
Computational Optimization and Applications, Vol. 79 (2021), 101--125.

\item {\em On the removal of weak compactness arguments in proof mining} (with F. Ferreira and P. Pinto) \\
Advances in Mathematics, Vol. 354 (2019), 106728, 55p.

\item {\em Effective strong convergence of the proximal point algorithm in CAT(0) spaces}
  (with A. Sipo\c s), \\
 Journal of Nonlinear and Variational Analysis, Vol. 2 (2018), No. 2, 219--228.\\
 Special Issue dedicated to Simeon Reich.

\item {\em An abstract proximal point algorithm}
(with A. Nicolae and A. Sipo\c s), \\
Journal of Global Optimization, Vol. 72 (2018), No. 3, 553-577.

\item {\em Quantitative results on Fej\'{e}r monotone sequences} (with U. Kohlenbach and A. Nicolae),\\
Communications in Contemporary Mathematics, Vol.  20 (2018), 1750015 [42 pages].

\item {\em A note on an alternative iterative method for nonexpansive mappings} (with A. Nicolae),\\
Journal of Convex Analysis, Vol. 24 (2017), No. 2, 501-503.

\item {\em Quantitative results on the Ishikawa iteration of Lipschitz pseudo-contractions} 
(with V. Radu and A. Sipo\c s),\\ 
Journal of Nonlinear and Convex Analysis, Vol. 17 (2016), No. 11, 2277-2292.

\item {\em Effective results on nonlinear ergodic averages in CAT(k) spaces} (with A. Nicolae),\\
Ergodic Theory and Dynamical Systems, Vol.  36 (2016), No. 8, 2580-2601.

\item {\em A note on an ergodic theorem in weakly uniformly convex geodesic spaces} (with A. Nicolae),\\
Archiv der Mathematik, Vol. 105 (2015), No. 5, 467-477.

\item {\em A rate of asymptotic regularity for the Mann iteration of $\kappa$-strict pseudo-contractions} (with D. Ivan), \\
Numerical Functional Analysis and Optimization, Vol. 36 (2015), No. 6, 792-798.

\item {\em Firmly nonexpansive mappings in classes of geodesic spaces} (with D. Ariza-Ruiz and 
G. L\'opez-Acedo),\\
Transactions of the American Mathematical Society, Vol. 366 (2014), 4299-4322.

\item {\em An application of proof mining to nonlinear iterations},\\
Annals of Pure and Applied Logic, Vol. 165 (2014), No.9, 1484-1500.

\item {\em Effective results on compositions of nonexpansive mappings}  (with A. Nicolae),\\
Journal of Mathematical Analysis and Applications, Vol. 410 (2014), No. 2, 902-907.

\item  {\em Effective metastability of Halpern iterates in CAT(0) spaces} (with U. Kohlenbach), \\
Advances in Mathematics, Vol. 231 (2012), No. 5, 2526-2556.\\
 Addendum in Advances in Mathematics, Vol. 250 (2014), 650-651. 

\item {\em On the computational content of convergence proofs via Banach limits} (with U. Kohlenbach),\\
Philosophical Transactions of the Royal Society A, Vol. 370 (2012), No. 1971, 3449--3463, \\
Theme Issue {\em The foundations of computation, physics and mentality: the Turing legacy}.

\item {\em Alternative iterative methods for nonexpansive mappings, rates of convergence and application} 
(with V. Colao, G. L\'opez-Acedo and V. Martin-Marquez), \\
Journal of Convex Analysis, Vol. 18 (2011), No. 2, 465--487.

\item\label{as-ne}
 {\em Asymptotically nonexpansive mappings in uniformly convex hyperbolic 
spaces} (with U. Kohlenbach), \\
Journal of the European Mathematical Society, Vol. 12 (2010), No. 1, 71-92.

\item {\em Maximal residuated lattices with lifting Boolean center } 
(with G. Geor-gescu and C. Mure\c san),\\
Algebra Universalis, Vol. 63 (2010), No. 1, 83-99.

\item  {\em A quantitative Mean Ergodic Theorem for uniformly convex Banach spaces} (with U. Kohlenbach),\\
 Ergodic Theory and Dynamical Systems, Vol. 29 (2009), No. 6, 1907-1915.

\item\label{Halpern-as-reg}
{\em Rates of asymptotic regularity for Halpern iterations of nonexpansive mappings},\\
Journal of Universal Computer Science,  Vol. 13 (2007), No. 11, 1680-1691;\\
in C.S. Calude, G. Stef\u{a}nescu, and M. Zimand (Editors): Combinatorics and Related Areas. A Collection of Papers in Honor of the 65th Birthday of Ioan Tomescu.

\item \label{AFPP-product} {\em The approximate fixed point property  in product spaces} (with U. Kohlenbach), \\
Nonlinear Analysis Series A: Theory, Methods \& Applications,  Vol. 66 (2007), No. 4, 806-818.

\item\label{quadratic} {\em A quadratic rate of asymptotic regularity in CAT(0)-spaces}, \\
Journal of Mathematical Analysis and Applications, Vol. 325 (2007), No. 1, 386-399.

\item {\em Baer extensions of BL-algebras}, \\
Journal of Multiple-Valued Logic and Soft Computing, Vol. 12 (2006), No. 3-4,  321-336.

\item {\em Sheaf representations of BL-algebras}, \\ Soft Computing - A Fusion of Foundations, Methodologies and Applications, Vol. 9, No. 12 (2005),  Special issue on BL-algebras, 897-909.

\item \label{ps-hoops} {\em Pseudo-hoops} (with G. Georgescu and V. Preoteasa), \\ Journal of Multiple-Valued Logic and Soft Computing, Vol. 11 (2005), No. 1-2, 153-184.

\item\label{compact}{\em  Compact representations of BL-algebras} (with A. Di Nola), \\ 
Archive for Mathematical Logic, Vol. 42 (2003),  No. 8, 737 - 761.


\item \label{LL+Ulrich-AAA} {\em Mann iterates of directionally nonexpansive mappings in hyperbolic spa-ces} (with  U. Kohlenbach),\\
Abstract and Applied Analysis, Vol. 2003 (2003), 449-477.

\item {\em The prime and maximal spectra and the reticulation of BL-algebras}, \\ 
Central European Journal of Mathematics, Vol. 1 (2003), No. 3, 382-397.

\item\label{3-modal} {\em Canonical models and filtrations in three-valued propositional modal logic}, \\
Journal of Multiple-Valued Logic, Vol. 8 (2002), No. 1-2, 577-590.

\item \label{classes-psBL} {\em Some classes of pseudo-BL algebras} (with  G. Georgescu), \\
Journal of Australian Mathematical Society, Vol. 73 (2002), No. 1, 127-153.

\item \label{Boolean-prod} {\em Boolean products of BL-algebras} (with A. Di Nola and G. Georgescu),\\
Journal of Mathematical Analysis and Applications, Vol. 251 (2000), No. 1, 106-131.


\end{enumerate}


\section{Conference, Workshop Papers}\label{conf}


\begin{enumerate}

\item \label{R-trees-hyp-spaces}
 {\em Proof mining in ${\mathbb R}$-trees and hyperbolic spaces},\\
Electronic Notes in Theoretical Computer Science, Vol. 165 (2006), Elsevier, 95-106;\\
in G. Mints and R. de Queiroz (Editors): Proceedings of the 13th Workshop on Logic, Language, 
Information and Computation (WOLLIC 2006), Stanford University, CA, USA, 18-21 July 2006.

\item \label{CAV}{\em Certifying optimality of state estimation programs} (with  
G. Ro\c su, R. Prasad Venkatesan  and J. Whittle),\\
Lecture Notes in Computer Science, Vol. 2725 (2003), Springer, 301-314;\\
in W. A. Hunt Jr., F. Somenzi (Editors): Computer Aided Verification (CAV), Proceedings of the 15th 
International Conference, Boulder, CO, USA, 8-12 July 2003, Proceedings.


\end{enumerate}

\section{Technical Reports and Preprints}\label{other}

\begin{enumerate}

\item {\em Quantitative asymptotic regularity and $T$-asymptotic regularity for the inexact generalized Halpern iteration} (with N. Dumitru), arXiv:2603.17105 [math.OC] (2026).

\item {\em Quantitative results on a generalized viscosity approximation method} (with P. Firmino), arXiv:2512.09968 [math.OC] (2025).

\item {\em Matching logic - a new axiomatization} (with D. Trufa\c s), arXiv:2506.13801 [cs.LO] (2025).

\item {\em Notes on applicative matching logic}, arXiv:2506.10088 [cs.LO] (2025).

\item {\em Barycenters in uniformly convex geodesic spaces}
(with A. Nicolae and A. Zaharescu), \\
arXiv:1609.02589 [math.MG] (2016).

\item {\em Proof mining in fixed point theory and ergodic theory},\\
 Oberwolfach Preprints OWP 2009-05, Mathematisches Forschungsinstitut Oberwolfach, Germany, 71pp (2009).
 
\item \label{LL+luta}
{\em Certifying Kalman Filters} (with G. Ro\c su),\\
 RIACS Technical Report TR.03.02, Research Institute for Advanced Computer Science (RIACS), 
 NASA Ames Research Center, Moffet Field, CA, USA, 53pp (2003).
 
\end{enumerate}


\section{Published abstracts}

\begin{enumerate}

\item {\em Proof mining and asymptotic regularity} (with P. Firmino), \\
2024 European Summer Meeting of the Association for Symbolic Logic, Logic Colloquium 2024, June 24-28, 2024, University of Gothenburg; \\
Bulletin of Symbolic Logic,  Vol. 30 (2024), No. 4, 600.\\

\item {\em Proof mining and the viscosity approximation method} (with P. Firmino), \\
2023 European Summer Meeting of the Association for Symbolic Logic, Logic Colloquium 2023, June 5-9, 2023, University of Milan; \\
Bulletin of Symbolic Logic 2024,  Vol. 30 (2024),  No. 1, 124.\\

\item {\em Proof mining and asymptotic regularity} (with H. Cheval, P. Firmino, U. Kohlenbach and P. Pinto),\\
Oberwolfach Reports, Vol. 20 (2023), No.  4, European Mathematical Society Publishing House, 3030-3033.

\item {\em Proof theoretic methods in nonlinear analysis III. Quantitative results on F\'ejer monotone sequences} (with U. Kohlenbach and A. Nicolae),\\
Oberwolfach Reports, Vol. 11 (2014), No. 4, European Mathematical Society Publishing House, 2960-2961.

\item {\em Recent developments in proof mining} (with U. Kohlenbach),\\
Oberwolfach Reports, Vol. 8 (2011), No. 4, European Mathematical Society Publishing House, 2982-2984.

\item {\em Recent results in proof mining} (with U. Kohlenbach),\\
Oberwolfach Reports, Vol. 5 (2008), No.  2, European Mathematical Society Publishing House, 929-931.

\item {\em Proof mining in CAT(0)-spaces and ${\mathbb R}$-trees}, \\
Abstracts of Papers presented to the American Mathematical Society, Volume 28, No. 1, Issue 147, AMS, 2007, 16.

\item {\em Approximate fixed points of nonexpansive functions in product spaces} (with U. Kohlenbach),\\
Mathematics, Algorithms, Proofs, Dagstuhl Seminar Proceedings 5021  (2006), pp.1-5 Schloss Dagstuhl - Leibniz-Zentrum f\"ur Informatik.

\item {\em Approximate fixed point property in product spaces} (with U. Kohlenbach),\\
 Oberwolfach Reports, Vol. 2 (2005), No. 1 , European Mathematical Society Publishing House, 795-797.


\end{enumerate}



\section{Editing}

\begin{enumerate}
\item Editor (together with  M. Marin) of: Proceedings of the 8th Symposium on Working Formal Methods (FROM 2024), EPTCS 410, 10.4204/EPTCS.410 (2024).
\item Editor (together with  H. Cheval and A. Sipo\c{s}) of: Proceedings of the 7th Symposium on Working Formal Methods (FROM 2023), EPTCS 389, DOI: 10.4204/EPTCS.389 (2023).
\item Guest editor (together with J. Kleijn and D. Lucanu) of:  Special Issue on The Working Formal Methods Symposium (FROM 2018),  Fundamenta Informaticae, Vol. 173 (2020), No. 2-3.
\end{enumerate}

\end{document}